---
output: 
  github_document
encoding: 'UTF-8'
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/",
  comment = NA
)
```

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/m-clark/confusionMatrix.svg?branch=master)](https://travis-ci.org/m-clark/confusionMatrix)
  [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/m-clark/confusionMatrix?branch=master&svg=true)](https://ci.appveyor.com/project/m-clark/confusionMatrix)
  [![Codecov test coverage](https://codecov.io/gh/m-clark/confusionMatrix/branch/master/graph/badge.svg)](https://codecov.io/gh/m-clark/confusionMatrix?branch=master)
  [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-experimental-blue.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- <a href="https://github.com/m-clark/confusionMatrix" alt="Miscellaneous Shenanigans"> -->
<!--         <img src="https://img.shields.io/badge/Status-Meh-ff5500.svg?colorA=00aaff&longCache=true&style=for-the-badge"  width=20.5%/></a> -->

 <!-- badges: end -->
 
<span class="" style = "height: 3em"></span>

# confusionMatrix

<br>

Given predictions and a target variable, provide numerous statistics from the resulting confusion matrix. The goal is to provide a wealth of summary statistics that can be calculated from a single confusion matrix, and return <span class="emph" style = "">**tidy**</span> results with as few dependencies as possible.




```{r demo}
library(confusionMatrix)

p = sample(letters[1:2], 250, replace = T, prob = 1:2)
o = sample(letters[1:2], 250, replace = T, prob = 1:2)

result = confusion_matrix(
  prediction = p,
  target = o,
  return_table = TRUE
)

result

result$Accuracy$`Frequency Table`
```

```{r demo-longer}
result = confusion_matrix(
  prediction = p,
  target = o,
  longer = TRUE
)

result
```


### Installation

To install from GitHub the <span class="pack">devtools</span> package is required.

```{r eval=FALSE}
devtools::install_github('m-clark/confusionMatrix')
```
