---
output: 
  github_document
encoding: 'UTF-8'
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  fig.path = "man/figures/",
  comment = NA
)
```

<!-- badges: start -->
  [![Travis build status](https://travis-ci.org/m-clark/confusionMatrix.svg?branch=master)](https://travis-ci.org/m-clark/confusionMatrix)
  [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/m-clark/confusionMatrix?branch=master&svg=true)](https://ci.appveyor.com/project/m-clark/confusionMatrix)
  [![Codecov test coverage](https://codecov.io/gh/m-clark/confusionMatrix/branch/master/graph/badge.svg)](https://codecov.io/gh/m-clark/confusionMatrix?branch=master)
  [![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-experimental-blue.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- <a href="https://github.com/m-clark/confusionMatrix" alt="Miscellaneous Shenanigans"> -->
<!--         <img src="https://img.shields.io/badge/Status-Meh-ff5500.svg?colorA=00aaff&longCache=true&style=for-the-badge"  width=20.5%/></a> -->

 <!-- badges: end -->
 

# confusionMatrix

<br>

A hopefully straightforward re-implementation inspired by the `caret` package to
simplify input and return 'tidy' results with as few dependencies as possible.
The goal is to provide a wealth of simple(!) summary statistics that can be
calculated from a single confusion matrix.


```{r demo}
library(confusionMatrix)

p = sample(letters[1:4], 250, replace = T, prob = 1:4)
o = sample(letters[1:4], 250, replace = T, prob = 1:4)

result = confusion_matrix(
  prediction = p,
  observed = o,
  return_table = TRUE
)

result

dplyr::glimpse(result$`Accuracy and Agreement`)
dplyr::glimpse(result$Other)
```

### Installation

To install from GitHub the <span class="pack">devtools</span> package is required.

```{r eval=FALSE}
devtools::install_github('m-clark/confusionMatrix')
```
